---
title: "ADRIÁN CONTURSI REYNOSO"
subtitle: "Political and Data Scientist | GIS Developer"
date: "April 2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, results = 'asis')

# Packages
library(dplyr)
library(googlesheets4)
library(pagedown)
library(glue)
library(tidyr)
library(knitr)

# Connect and Download the Google Drive Sheet
gs4_deauth()
cv_data <- read_sheet("https://docs.google.com/spreadsheets/d/11t8QEBrF6-aY2Fgm2jB3XCWtutS3OpCHmpzoawU7fbY/edit?usp=sharing")
cv_data <- data.frame(cv_data)

# Choose the Language for the CV
cv_data <- cv_data %>%
  filter(Language == "English") # English or Spanish
```

acontursi@ideasphi.com

[Personal Website](http://www.adriancontursi.com.ar)

Adrián Contursi is a political scientist and data scientist, passionate about the intersection between State, Democracy and New Technologies. 

He has worked for international organizations, mainly in political analysis of the situation and in understanding the impact of social networks on polarization and governance.

He is an academic researcher and professor at the Universidad Nacional del Litoral and the Universidad Autónoma de Entre Ríos, where he teaches Statistics, Social Research, Political and Electoral Geography, and Social Network Analysis Methodology.


## WORK EXPERIENCE


## EDUCATION
```{r}
education <- cv_data %>%
  filter(Section == "Education") %>%
  select(Year, Degree, Institution, Location)
knitr::kable(education)
```

## RESEARCH
# Membership
```{r}
research <- cv_data %>%
  filter(Section == "Research") %>%
  select(Year, Position, Center, Institution, Location)
knitr::kable(research)
```

# Projects
```{r}
research <- cv_data %>%
  filter(Section == "Research_Project") %>%
  select(Year, Project, Center, Institution, Director, Funding_by, Amount)
knitr::kable(research)
```

## TEACHING
## Latin American Faculty of Social Sciences
```{r}
flacso <- cv_data %>%
  filter(Section == "Teaching") %>%
  filter(Type == "FLACSO") %>%
  select(Year, Position, Subject, Location)
knitr::kable(flacso)
```

## National Pedagogical University
```{r}
unipe <- cv_data %>%
  filter(Section == "Teaching") %>%
  filter(Type == "UNIPE") %>%
  select(Year, Position, Subject, Location)
knitr::kable(unipe)
```

## Franz Tamayo Private University (Bolivia)
```{r}
unifranz <- cv_data %>%
  filter(Section == "Teaching") %>%
  filter(Type == "UNIFRANZ") %>%
  select(Year, Position, Subject, Location)
knitr::kable(unifranz)
```

## Autonomous University of Entre Rios
```{r}
uader <- cv_data %>%
  filter(Section == "Teaching") %>%
  filter(Type == "UADER") %>%
  select(Year, Position, Subject, Location)
knitr::kable(uader)
```

## National University of the Litoral
```{r}
unl <- cv_data %>%
  filter(Section == "Teaching") %>%
  filter(Type == "UNL") %>%
  select(Year, Position, Subject, Location)
knitr::kable(unl)
```

## University of Buenos Aires
```{r}
uba <- cv_data %>%
  filter(Section == "Teaching") %>%
  filter(Type == "UBA") %>%
  select(Year, Position, Subject, Location)
knitr::kable(uba)
```

## Higher Education Institute No. 64 Ana Maria Fonseca
```{r}
ies64 <- cv_data %>%
  filter(Section == "Teaching") %>%
  filter(Type == "IES64") %>%
  select(Year, Position, Subject, Location)
knitr::kable(ies64)
```


## PUBLICATIONS
## Articles
```{r}
articles <- cv_data %>%
  filter(Type == "Article") %>%
  select(Year, Author, Detail, Publisher)
knitr::kable(articles)
```

## Chapters
```{r}
chapters <- cv_data %>%
  filter(Type == "Chapter") %>%
  select(Year, Author, Detail, Publisher)
knitr::kable(chapters)
```

## Papers at Congress, Conferences and Seminars
```{r}
papers <- cv_data %>%
  filter(Type == "Paper") %>%
  select(Year, Author, Detail, Event)
knitr::kable(papers)
```


## COURSES
## Courses taught
```{r}
research <- cv_data %>%
  filter(Section == "Teaching") %>%
  filter(Type == "Course") %>%
  select(Year, Detail, Institution, Location)
knitr::kable(research)
```

## Specializations
```{r}
research <- cv_data %>%
  filter(Section == "Course") %>%
  select(Year, Detail, Institution, Location)
knitr::kable(research)
```


## ACADEMIC EVENTS
```{r}
research <- cv_data %>%
  filter(Section == "Event") %>%
  select(Year, Event, Institution, Location)
knitr::kable(research)
```
